Response to reviewers

### 2022-03-29 reviews/EJOR/01/main.tex
Address another two comments
- More applications examples
- Rewritten highlights
Address the final comments

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 9: \textit{Page 22 scenario at bottom of
        the page: this scenario does not seem like a realistic scenario:
        the mean number of patients offered per time unit is larger than
        that can be treated, meaning that many patients would be rejected
        by the hospital. Please comment on the reality of the selected
        scenarios}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed.

@@

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 4: \textit{The authors claim their model
        has applications in a range of sectors and settings, but have given
        no examples.}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed.

@@

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 1: \textit{Rewrite the Highlights (for
        review) of the paper, and really capture the sense of work.}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 5: \textit{There are some mistakes/typos
        with English grammar and writing in the article.}
    \end{itemize}
    TBA % TODO: Reply to this comment once addressed

>>>>

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 9: \textit{Page 22 scenario at bottom of
        the page: this scenario does not seem like a realistic scenario:
        the mean number of patients offered per time unit is larger than
        that can be treated, meaning that many patients would be rejected
        by the hospital. Please comment on the reality of the selected
        scenarios}
    \end{itemize}
    The queueing systems in the particular example are meant to be very
    busy systems. In the new manuscript it is more clearly stated.

@@

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 4: \textit{The authors claim their model
        has applications in a range of sectors and settings, but have given
        no examples.}
    \end{itemize}
    Examples of other applications have been added in the conclusion section
    of the manuscript.

@@

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 1: \textit{Rewrite the Highlights (for
        review) of the paper, and really capture the sense of work.}
    \end{itemize}
    Highlights have been rewritten to be more explicit in terms of the work
    that was done.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 5: \textit{There are some mistakes/typos
        with English grammar and writing in the article.}
    \end{itemize}
    We have thoroughly checked the grammar and spelling of the manuscript.
